Cognate Priming

### 2023-05-03 docs/index.qmd
Fix targets workflow

# load packages
library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(purrr)
library(lubridate)
library(ggplot2)
library(gt)
library(tidybayes)
library(brms)
library(polypoly)
library(tidytext)
library(janitor)
library(forcats)
library(scales)
library(patchwork)
library(bvqdev)

@@

We collected vocabulary data from participants. In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI, @hamilton2000infant] two weeks before each appointment. In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvqdev) immediately after the appointment, and were given two weeks to fill it. In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language. In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists. All checklists included the words involved in the trial lists. When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*. Each response to either checklist was aggregated to produce several vocabulary measures:

>>>>

# load packages
library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(purrr)
library(lubridate)
library(ggplot2)
library(gt)
library(tidybayes)
library(brms)
library(polypoly)
library(tidytext)
library(janitor)
library(forcats)
library(scales)
library(patchwork)
library(bvq)

@@

We collected vocabulary data from participants. In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI, @hamilton2000infant] two weeks before each appointment. In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvq) immediately after the appointment, and were given two weeks to fill it. In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language. In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists. All checklists included the words involved in the trial lists. When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*. Each response to either checklist was aggregated to produce several vocabulary measures:
